The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-03-29 doc/paper/skysubtraction.tex
Wednesday's lunch update

The first step in object extraction is a simple tophat aperture (boxcar) 
extraction centered at the fiber positions determined from the flat-field 
and with a full spatial width of 6 CCD pixels.  The median counts per fiber 
are passed directly to a test for overly bright fibers. Fiber spectra are 
identified as bright (a.k.a. "WHOPPING") if the median counts per pixel in the 
boxcar extraction is greater than 10000 counts above the median counts in the 
frame.  In addition, only the brightest fiber in a spatially continuous set of 
bright fibers is labelled "WHOPPING".

\begin{enumerate}
\item{Locate bright fibers (aka whopping fibers)}
\item{Assess sky fiber levels}
\item{Commence iterative Optimal extraction }
\item{Shift wavelength solution to match sky lines (describe in wavelength solution)}
\item{Sky subtract}

Note: Flux correction and Telluric correction have been moved (a long time ago).

>>>>

The first step in object extraction is a simple tophat aperture (boxcar) 
extraction centered at the fiber positions determined from the flat-field 
and with a full spatial width of 6 CCD pixels.  The median counts per fiber 
are passed directly to a test for overly bright fibers. Fiber spectra are 
identified as bright (a.k.a. "WHOPPING") if the median counts per pixel in the 
boxcar extraction are greater than 10000 counts above the median in the 
frame.  In addition, only the brightest fiber in a spatially contiguous set of 
bright fibers is labelled "WHOPPING".

A pixelmask vector is created for each fiber spectrum to be extracted.
See Appendix ?? for a description of the mask bits and their use.

We fit for a slight distortion of the stored flat-field fiber traces to 
best match the fiber positions of the science image.  Nominal shifts and
distortions are usually less than a native CCD pixel.  The science frame
is now extracted in a series of 6 steps which we detail below.

\begin{enumerate}
\item{Initial extraction including broad wings of bright (WHOPPING) fibers.}
\item{Reconstruct a smooth background light model based on fitted parameters.}
\item{Calculate a scattered halo image using the model of the fiber spectra less
the aforementioned smooth background.}
\item{Re-extract fiber spectra on the scattered halo subtracted image.}
\item{Reconstruct smooth background and subtract.}
\item{Final extraction with no free parameters in the background and
no free parameters in the profile widths.}
\end{enumerate}

The extracted science spectra are first normalized by the fiber flat vectors.
Strong atmospheric emission lines (sky lines) are identified in the the 
set of spectra, and the wavelength solution is shifted to match the 
identified lines.  Examples of the shift corrections are shown in Figure ??.  
The widths of the identified sky lines are also measured with the same method
as the arc-line width measurements.  All spectra are also normalized by
the average flat-field spectrum (the superflat) to remove small scale
features likely attributed to the chromatic response of the dichroic.
The wavelength solution is corrected to both vacuum wavelengths and the
heliocentric velocity frame.
